MCLM parameters, interactive example

### 2024-05-20 apps/Graphical_representation_interactive.qmd
Cleans up code of the plot renders

draw_spikes <- reactiveVal() # Flag to indicate whether to draw spikes (for
                             #   single value plotting only)
observeEvent( ## TODO: Draw spikes
  input$sample_type,
  draw_spikes(input$sample_type == "unique value")
)
# Constant objects:
LIM_INF <- -3L
LIM_SUP <-  3L
LIMITS  <- c(LIM_INF, LIM_SUP)
BREAKS  <- LIM_INF:LIM_SUP

@@

# Render scatter plot in transformed coordinates:
output$ts_original <- renderPlot({
})
output$ls_transformed <- renderPlot({

@@

  ## Basis vectors:
  basis_vec_1 <- transf_matrix()[, 1]
  basis_vec_2 <- transf_matrix()[, 2]
  basis_vec_1_norm <- basis_vec_1^2 |> sum() |> sqrt()
  basis_vec_2_norm <- basis_vec_2^2 |> sum() |> sqrt()

@@

  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_2` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = BREAKS * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_2[2] + LIM_INF * basis_vec_1[2],
      labels       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})
output$ts_transformed <- renderPlot({
})
```

>>>>

# Constant objects:
LIM_INF <- -3L
LIM_SUP <-  3L
LIMITS  <- c(LIM_INF, LIM_SUP)
BREAKS  <- LIM_INF:LIM_SUP

@@

output$ts_original <- renderPlot({
})

# Render scatter plot in transformed coordinates:
output$ls_transformed <- renderPlot({

@@

  ## Basis vectors:
  basis_vec_1 <- transf_matrix()[, 1]
  basis_vec_2 <- transf_matrix()[, 2]

@@

  # Render plot:
  lt_sample_transf() |> ggplot(aes(x = theta_1, y = theta_2)) +
    geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
    geom_abline( # Oblique `theta_1` axis
      intercept = 0,
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH
    ) +
    geom_abline( # Oblique panel grid lines
      intercept = BREAKS * basis_vec_2[2],
      slope     = tan_vec_1,
      linewidth = LINE_WIDTH,
      linetype  = "C6"
    ) +
    geom_point(alpha = .5) +
    scale_x_continuous(
      limits       = LIMITS,
      breaks       = BREAKS,
      minor_breaks = NULL,
      name         = NULL,
      oob          = oob_keep
    ) +
    scale_y_continuous(
      limits       = LIMITS,
      breaks       = BREAKS * basis_vec_2[2] + LIM_INF * basis_vec_1[2],
      labels       = BREAKS,
      name         = NULL,
      oob          = oob_keep
    ) +
    coord_fixed(expand = FALSE, clip = "on") +
    theme(
      axis.line          = element_blank(),
      panel.grid.major.x = element_line(
        color     = "black",
        linewidth = LINE_WIDTH,
        linetype  = "C6"
     )
    )
})
output$ts_transformed <- renderPlot({
})
```
